Baseline centering problem

### 2018-12-12 paper/tangotd.tex

>>>>

In the end we should perhaps just learn a representation of $\Delta^{-1}$
in a hidden state that represents distributions on $s$ (trained to
faithfully reproduce averages of functions). $\Delta^{-1}$ satisfies the
two-sided equation $\Delta^{-1}=\Id+\Delta^{-1}P=\Id+P\Delta^{-1}$, so
when observing a transition $s\to s'$ we both update the model of
how to arrive at $s'$ and of what happens when starting at $s$.
